ManuscriptFigures

### 2024-03-15 Code/Plots_Growth.Rmd
Generated compressed .tiff files

ggsave(file = file.path(PlotsOutPLOS, "Fig1.tiff"), plot = PurParPlot, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

@@

ggsave(file = file.path(PlotsOutPLOS, "S2_Fig.tiff"), plot = deltaODLogGrowthPlot, device = NULL, scale = 1, height=20, width= 30, units = c("cm"),dpi = 300, limitsize = TRUE)

@@

ggsave(file = file.path(PlotsOutPLOS, "Fig3.tiff"), plot = MED4PAR, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

@@

ggsave(file = file.path(PlotsOutPLOS, "Fig5.tiff"), plot = SS120PAR, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

@@

ggsave(file = file.path(PlotsOutPLOS, "Fig7.tiff"), plot = MIT9313PAR, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

@@

ggsave(file = file.path(PlotsOutPLOS, "S3_Fig.tiff"), plot = OverlayPlots, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, limitsize = TRUE)

>>>>

ggsave(file = file.path(PlotsOutPLOS, "Fig1.tiff"), plot = PurParPlot, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE)

@@

ggsave(file = file.path(PlotsOutPLOS, "S2_Fig.tiff"), plot = deltaODLogGrowthPlot, device = NULL, scale = 1, height=20, width= 30, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE)

@@

ggsave(file = file.path(PlotsOutPLOS, "Fig3.tiff"), plot = MED4PAR, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE)

@@

ggsave(file = file.path(PlotsOutPLOS, "Fig5.tiff"), plot = SS120PAR, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE)

@@

ggsave(file = file.path(PlotsOutPLOS, "Fig7.tiff"), plot = MIT9313PAR, device = NULL, scale = 1, height=20, width= 35, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE)

@@

ggsave(file = file.path(PlotsOutPLOS, "S3_Fig.tiff"), plot = OverlayPlots, device = NULL, scale = 1, height=25, width= 35, units = c("cm"),dpi = 300, compression = "lzw", limitsize = TRUE)
